Constraining Quiescent Supermassive Black Hole Environments.

### 2014-08-11 ms.tex
New figure and table

\item \emph{Type Ia SNe} Following \citealt{ShcherbakovWong+:2014a}, the energy injected per Ia SNe is $E_{\rm Ia}=10^{51}$ ergs, and the SNe rate is $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$.

@@

 Following \citealt{ShcherbakovWong+:2014a}, $E_{\rm Ia}=10^{51}$ ergs and $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$, which gives $eta\simeq 230 \eta^{-1/2}$ km/s (For $\eta=0.1$ this corresponds to $\vwO\simeq$ 500 km/s.   
 %Perhaps it would be best to adopt a fiducial eta=0.1--this may be more straightforward from the pov of both heating and cooling.

@@

There will be some radius, $r_{\rm Ia}$, where the dynamical timescale of the flow becomes comparable to the time between successive Type Ia SNe.  If the stagnation radius of the flow is outside of $\rIa$ then SNes will provide a steady contribution to $\vwO$

@@

%AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...

@@

Note MSPs may also be dissociated in the galactic center...
%%Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.
\end{enumerate}

@@

In principle, the gas should radiatively cool as well--either from metal line cooling for $T\lsim 2\times 10^7$ K, or through free-free emission for $T\gsim 2\times 10^7$ K.  If the cooling rate is much smaller than the rate of energy injection then radiative cooling may be safely neglected.

@@

For $\vwO$=1000 km/s, it is apparent from Figure~\ref{fig:cooling}, that radiative cooling may be safely neglected. With a few exceptions this is also true for $\vwO$=500 km/s.  However, for $\vwO$=200 km/s cooling may be quite important. However, at smaller $\eta$ the effects of cooling will be less pronounced. For each of our galaxies we give the maximum $\eta$ such that $H/C >$1 in Table .  Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling. $\eta$ depends on the age of the stellar population, and will realistically vary between $\sim 0.1$ and $\sim 1$.

>>>>

\item \emph{Type Ia SNe} From he energy injected per Ia SNe, $E_{\rm Ia}d}$ ergs, and the SNe rate,  $R_{\rm Ia}

@@

 Following \citealt{ShcherbakovWong+:2014a}, $E_{\rm Ia}=10^{51}$ ergs and $R_{\rm Ia}\simeq 4 \times 10^{-14} \Msun^{-1}$ yr$^{-1}$, which gives $\vwO\simeq 230 \, \eta^{-1/2}$ km/s (For $\eta=0.1$ this corresponds to $\vwO\simeq$ 500 km/s.   
 %Perhaps it would be best to adopt a fiducial eta=0.1--this may be more straightforward from the pov of both heating and cooling.

@@

There will be some radius, $r_{\rm Ia}$, where the dynamical timescale of the flow becomes comparable to the time between successive Type Ia SNe.  If the stagnation radius ($\rs$) of the flow is outside of $\rIa$ then SNes will provide a steady contribution to $\vwO$

@@

...

%%AG-Plot comparing stagnation radius and Ia radius for all profiles...I found this to be confusing/hard to explain.
%AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...

@@

Also, MSPs may also be dissociated in the galactic center...
%%Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.
\end{enumerate}

@@

The gas should radiatively cool as well--either from metal line cooling for $T\lsim 2\times 10^7$ K, or through free-free emission for $T\gsim 2\times 10^7$ K.  However, if the cooling rate is much smaller than the rate of energy injection then radiative cooling may be safely neglected.

@@

For $\vwO$=1000 km/s, it is apparent from Figure~\ref{fig:cooling}, that radiative cooling may be safely neglected. With a few exceptions this is also true for $\vwO$=500 km/s.  However, for $\vwO$=200 km/s cooling may be quite important. For smaller $\eta$ the effects of cooling will be less pronounced. For each of our galaxies we give the maximum $\eta$ such that $H/C >$1 in Table .  Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling. $\eta$ depends on the age of the stellar population, and will realistically vary between $\sim 0.1$ and $\sim 1$.

\input{figures/eta_tab.tex}
